---
title: "p8105_hw5_yc3731"
author: "Yue Chen"
date: "11/17/2020"
output: github_document
---

```{r setup, include=FALSE}
library(tidyverse)

knitr::opts_chunk$set(
  fig.width = 6,
  fig.asp = .6,
  out.width = "90%"
)
theme_set(theme_minimal() + theme(legend.position = "bottom"))
options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)
scale_colour_discrete = scale_color_viridis_d
scale_fill_discrete = scale_fill_viridis_d
```

## Problem 1

Import dataset.
```{r}
homecide = read.csv("./data/homicide-data.csv")
```

Describe dataset.

The raw dataset has `r nrow(homecide)` observations and `r ncol(homecide)` columns. 
Variables in the dataset include `r names(homecide)`. 

Create a new variable.
```{r}
homecide = 
  homecide %>%
  mutate(city_state = str_c(city, ", ", state))
```

Summarize within cities to obtain the total number of homicides and the number of unsolved homicides.
```{r}
homecide_df =
  homecide %>%
  mutate(
    resolved = case_when(
      disposition == "Closed without arrest" ~ "unsolved", 
      disposition == "Open/No arrest"        ~ "unsolved",
      disposition == "Closed by arrest"       ~ "solved"
    )
  ) %>%
  select(city_state, resolved) %>%
  filter(city_state != "Tulsa, AL")

aggregate_df = 
  homecide_df %>%
  group_by(city_state) %>%
  summarise(
    hom_total = n(), 
    hom_unsolved = sum(resolved == "unsolved")
  )
```

For the city of Baltimore, MD, estimate the proportion of homicides that are unsolved.
```{r}
prop.test(
  aggregate_df %>%
    filter(city_state == "Baltimore, MD") %>%
    pull(hom_unsolved), 
  aggregate_df %>%
    filter(city_state == "Baltimore, MD") %>%
    pull(hom_total)
  )%>%
    broom::tidy()
```

Iterate the test for each city in the dataset.
```{r}
results_df = 
  aggregate_df %>%
  mutate(
    prop_tests = map2(.x = hom_unsolved, .y = hom_total, ~prop.test(x = .x, n = .y)), 
    tidy_tests = map(.x = prop_tests, ~broom::tidy(.x))
  ) %>%
  select(-prop_tests) %>%
  unnest(tidy_tests) %>%
  select(city_state, estimate, conf.low, conf.high)
```

Create a plot that shows the estimates and CIs for each city.
```{r}
results_plot = 
  results_df %>%
  ggplot(aes(x = reorder(city_state, estimate), y = estimate)) + 
  geom_point() + 
  geom_errorbar(aes(ymin = conf.low, ymax = conf.high)) +
  theme(axis.text.x = element_text(angle = 80, hjust = 1)) +
  labs(
    title = "Estimates and CIs of unsolved homecides for each city", 
    x = "city", 
    y = "proportions of unsolved homecides"
  )

results_plot
```

## Problem 2

Import and tidy data.
```{r}
study_data = 
  tibble(file_name = list.files(path = "./data/data")) %>%
  mutate(name = map(.x = str_c("./data/data/", file_name), ~read_csv(.x))) %>%
  unnest() %>%
  separate(file_name, into = c("arm", "id"), sep = "_", remove = F) %>%
  gather(key = week, value = observation, week_1:week_8) %>%
  mutate(
    week = str_replace(week, "week_", ""),
    file_name = str_replace(file_name, ".csv", ""), 
    id = str_replace(id, ".csv", "")
  )
```

Make a spaghetti plot showing observations on each subject over time.
```{r}
spaghetti_plot = 
  study_data %>%
    ggplot(
      aes(x = week, y = observation, group = file_name, col = arm)
    ) + 
    geom_line() +
    labs(
      title = "Observations on each subject over time",
      x = "week", 
      y = "observation"
    ) + 
    theme(legend.position = "bottom")

spaghetti_plot
```
In general, patients in control arm have lower weekly observations than patients in experimental arm.
Some patients in control and experiment arms have similar weekly observations.

